Abstraction and Invariance for Algebraically Indexed Types

### 2012-10-25 paper/section-introduction.tex
Add a paper-overview picture

>>>>

\begin{figure}
  \centering
  \begin{tikzpicture}
  \node at (-3,1) [rectangle,style={align=center}] {Algebraic \\ Theory};
  \node at (-2,1) {$+$};
  \node at (-0.5,1) [rectangle,style={align=center}] {Index-Erasure \\ Interpretation};
  \node at (1,1) {$+$};
  \node at (2.6,1) [rectangle,style={align=center}] {Relational \\ Interpretation};

  \draw plot (-4,0.8) .. controls (-4,0) and (-0.4,1) .. (-0.4,0)
             -- (-0.6,0) -- (0,-0.3) -- (0.6,0) --
             (0.4,0) .. controls (0.4,1) and (4,0) .. (4,0.8);

  \node at (0,-0.7) [rectangle,style={align=center}] {Abstraction Theorem (\thmref{thm:abstraction})};

  \draw plot (-0.8,-1) .. controls (-0.8,-1.3) and (-3.5,-1.5) .. (-3.5,-2)
             -- (-3.7,-2) -- (-3.1,-2.3) -- (-2.5,-2) -- 
             (-2.7,-2) .. controls (-2.7,-1.5) and (-0.8,-1.6) .. (-0.7,-1.5)
                       .. controls (-0.8,-1.6) and (-0.5,-1.5) ..
             (-0.4,-2) -- (-0.6,-2) -- (0,-2.3) -- (0.6,-2) --
             (0.4,-2) .. controls (0.5,-1.5) and (0.8,-1.6) .. (0.7,-1.5)
                      .. controls (0.8,-1.6) and (2.7,-1.5) ..
             (2.7,-2) -- (2.5,-2) -- (3.1,-2.3) -- (3.7,-2) -- (3.5,-2)
                      .. controls (3.5,-1.5) and (0.8,-1.3) .. (0.8,-1);

  \node at (-3.1,-2.8) [rectangle,style={align=center}] {Free \\ Theorems};
  \node at (0,-2.8) [rectangle,style={align=center}] {Type \\ Isomorphisms};
  \node at (3.1,-2.8) [rectangle,style={align=center}] {Non-definability};
\end{tikzpicture}
  \caption{Summary of the Paper}
  \label{fig:summary}
\end{figure}
